---
title: "Individual Portion: Streaming Data"
subtitle: "STT2860 F22 Project 03"
author: "Natara, Gracey, Evan"
date: "`r format(Sys.time(), '%A, %B %d, %Y @ %I:%M %p')`"
output: 
  html_document: 
    theme: cosmo
    highlight: textmate
    code_folding: hide
---

```{r globaloptions, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  comment = NA
)
```
***

## Setup

### Packages Used

```{r loadpackages}
library(tidyverse)
```

### Datasets Used

### Background of the Data

The datasets were downloaded from [Disney+ Movies and TV Shows | Kaggle](https://www.kaggle.com/datasets/shivamb/disney-movies-and-tv-shows) and [TV shows on Netflix, Prime Video, Hulu and Disney+ | Kaggle](https://www.kaggle.com/datasets/ruchi798/tv-shows-on-netflix-prime-video-hulu-and-disney). You can read about them there, including variable definitions, sources, when they were created, and other information. Load the two datasets and use `glimpse()` to explore their structures.

#### Disney+ Dataset

```{r loaddisneydata}
disneydata <- readRDS("/home/students/dulaneynl/STT2860/git_repo/STT2860F22project3/data/disneypluscontent.rds")
disneydata
```

#### Streaming Dataset

```{r loadstreamingdata}
streamingdata <- readRDS("/home/students/dulaneynl/STT2860/git_repo/STT2860F22project3/data/streamingcontent.rds")

```

<hr>

## Analyses

### Create the Analysis Datasets

#### Disney+ Dataset

Use `select()` to delete the variables `director`, `cast`, `country`, `listed in`, and `description` from the dataset.

```{r disneyedits}
  new_disney_data <- select(disneydata, -director, -cast, -country, -listed_in, -description)
  new_disney_data
```

#### Streaming Dataset

I used a function called `pivot_longer()` on the downloaded data to change the shape of the dataset. You will need to do additional necessary editing on the dataset before you analyze it.

* Use `filter()` to remove any row where `YesNo` is `0` (a `0` means it is *not* on the service).
* Use the `separate()` function to split `IMDb`. Separate the show rating from the max rating of `10`. 
* Use the `separate()` function to split `RottenTomatoes`. Separate the show rating from the max rating of `100`. 
* Use `mutate()` to convert the shows' IMDb and Rotten Tomatoes ratings into numerical variables instead of categorical.

```{r streamingedits}
  new_streamingdata <- streamingdata %>%
  filter(YesNo == 1) %>%
  separate(col = IMDb , into = c("IMDBdrating", "IMBdmax"), sep = "/") %>%
  separate(col = RottenTomatoes, into = c("RTrating", "RTmax"), sep = "/")

new_streamingdata
```